Niche complementarity among pollinators increases community-level plant reproductive success

### 2020-03-16 Network_structure_and_function.Rmd
change in readme to include location of .csv files

d<-all_interactions
dtrans<-subset(d, d$Out=="transect")  #keep only records within transects, eliminate focal and other records outside transects
f<-fruitset
s<-seedset

@@

Within each site, we marked between 3 and `r max(f.inds$tot.inds)` individuals (mean $\pm$ SD: `r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`, Table S2) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (mean $\pm$ SD:`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`, Table S2). For each individual, at the end of the season, we recorded fruit set (i.e. the proportion of flowers that set fruit), the average number of seeds per fruit and the average fruit and seed weight per fruit (`r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits subsampled, mean $\pm$ SD: `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`, Table S3). These last two variables show a strong correlation (Pearson correlation= 0.89), but we believe they provide complementary information. Our survey included a total of `r nlevels(f2$Plant.sp)` different totally or partially self-incompatible plant species that depend on pollinators to maximize their reproduction (Table S4) across our `r nlevels(f2$Site_ID)` sites. All plant species were shrubs selected to be common and widespread species, and individuals were selected depending on the presence of flowers during the sampling events. In addition to species-level values, we also calculated the average reproductive success at the site level. To that end, the values of reproductive success obtained at the species level were averaged per site.

@@

  Nestedness is the property by which specialists interact with a subset of the species that generalists interact with [@Bascompte2003]. Although there is an ongoing debate in the literature (e.g., [@James2012]), some theoretical studies have found that nested networks are more stable and resilient to perturbations because nestedness promotes a greater diversity by minimizing competition among species in a community [@Bastolla2009]. However, many network attributes vary with network size and complexity [@Bluthgen2006]. In the case of nestedness, we know it can be affected by network size and connectance [@Song2017a]. An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks. However, this approach has been shown to present the same issues, as z-scores also change with network size and connectance [@Song2017a]. We thus followed the advice provided by Song et al. (2017) by using a normalized value of the widely-used nestedness metric NODF based on binary matrices [@Almeida-Neto2011], $NODF_c$. This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance and S is network size, calculated as $S = \sqrt(ncol(web)*nrow(web))$. $NODF_n$ is calculated as $NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017a]. To calculate max(NODF) we used a corrected version of the algorithm [@Simmons2019a] whenever possible. Results did not change qualitatively when using the uncorrected version of the algorithm for all sites as both are highly correlated (Spearman correlation = 0.94).

@@

#calculate RELATIVE number of visits per plant sps
flower_count<-read.csv("Flower_Count_BeeFun_2015.csv")  ###############CAMBIAR POR BASE DE DATOS EN BEEFUN!
flower_count$Plant_gen_sps<-paste(flower_count$Plant.genus, flower_count$Plant.species)

>>>>

d<-all_interactions
dtrans<-subset(d, d$Out=="transect")  #keep only records within transects, eliminate focal and other records outside transects
f<-fruitset
s<-seedset
flower_count<-flowers

@@

Within each site, we marked between 3 and `r max(f.inds$tot.inds)` individuals (mean $\pm$ SD: `r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`, Table S2) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (mean $\pm$ SD:`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`, Table S2). For each individual, at the end of the season, we recorded fruit set (i.e. the proportion of flowers that set fruit), the average number of seeds per fruit and the average fruit and seed weight per fruit (`r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits subsampled, mean $\pm$ SD: `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`, Table S3). These last two variables show a strong correlation (Pearson correlation= 0.89), but we believe they provide complementary information. Our survey included a total of `r nlevels(f2$Plant.sp)` different totally or partially self-incompatible plant species that depend on pollinators to maximize their reproduction (Table S4) across our `r nlevels(f2$Site_ID)` sites. All plant species were shrubs selected to be common and widespread species. Individuals were selected depending on the presence of flowers during the sampling events. In addition to species-level values, we also calculated the average reproductive success at the site level. To that end, the values of reproductive success obtained at the species level were averaged per site.

@@

  Nestedness is the property by which specialists interact with a subset of the species that generalists interact with [@Bascompte2003]. Although there is an ongoing debate in the literature (e.g., [@James2012]), some theoretical studies have found that nested networks are more stable and resilient to perturbations because nestedness promotes a greater diversity by minimizing competition among species in a community [@Bastolla2009]. However, many network attributes vary with network size and complexity [@Bluthgen2006]. In the case of nestedness, we know it can be affected by network size and connectance [@Song2017a]. An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks. However, this approach has been shown to present the same issues, as z-scores also change with network size and connectance [@Song2017a]. We thus followed the advice provided by Song et al. (2017) by using a normalized value of the widely used nestedness metric NODF based on binary matrices [@Almeida-Neto2011], $NODF_c$. This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance and S is network size, calculated as $S = \sqrt(ncol(web)*nrow(web))$. $NODF_n$ is calculated as $NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017a]. To calculate max(NODF) we used a corrected version of the algorithm [@Simmons2019a] whenever possible. Results did not change qualitatively when using the uncorrected version of the algorithm for all sites as both are highly correlated (Spearman correlation = 0.94).

@@

#calculate RELATIVE number of visits per plant sps
flower_count$Plant_gen_sps<-paste(flower_count$Plant.genus, flower_count$Plant.species)
